data exploration

### 2021-04-26 outputs/exploratory.Rmd
shiny complete, train/test complete, first round of content edits done.

>>>>

```{r}
ddata <- expdata %>%
  dplyr::select(treatment,
                s1_sim, s1_tsr, 
                s2_sim, s2_tsr, 
                t2_sim1, t2_tsr,
                grade, std_grade, 
                t2_finalexam, f17_enrolled,
                obj_exam,
                s_firstgen,
                s_hisp_black,
                year,
                s_firstgen) %>%
  mutate(all = 1)

write_csv(ddata, here("takingittothenextlevel/ddata.csv"))
```

```{r}
teststudentfirstsimilaritymodel <- lm(data = expdata,
                                  formula = s1_sim ~ treatment + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                                     na.action = na.omit)
teststudentsecondsimilaritymodel <- lm(data = expdata,
                                   formula = s2_sim ~ treatment + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                                     na.action = na.omit)
teststudentsecondrelationshipmodel <- lm(data = expdata,
                                     formula = s2_tsr ~ treatment + s1_tsr + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                                     na.action = na.omit)
testteachersecondrelationshipmodel <- lm(data = expdata,
                                     formula = t2_tsr ~ treatment + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                                     na.action = na.omit)
testgrademodel <- lm(data = expdata,
                 formula = grade ~ treatment + s1_female + ir_f16_gpa + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                                     na.action = na.omit)
testexamgrademodel <- lm(data = expdata %>% filter(obj_exam == 1),
                     formula = t2_finalexam ~ treatment + s1_female + ir_f16_gpa + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                                     na.action = na.omit)
testteachersecondsimilarity <- polr(formula = as.factor(t2_sim1) ~ treatment + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                                data = expdata,
                                Hess = TRUE,
                                     na.action = na.omit)
testenrollmentfallmodel <- glm(data = expdata,
                           formula = f17_enrolled ~ treatment + s1_female + ir_f16_gpa + teacherid + s_female + s_race + s_firstgen + ir_f16_gpa + year,
                           family = "binomial",
                                     na.action = na.omit)
```

```{r testmodeltable, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
# Make table to display model results
stargazer(teststudentfirstsimilaritymodel,
          teststudentsecondsimilaritymodel,
          teststudentsecondrelationshipmodel,
          testteachersecondrelationshipmodel,
          testgrademodel,
          testexamgrademodel,
          testteachersecondsimilarity,
          testenrollmentfallmodel,
          title = "Replication model results",
          align = TRUE,
          ci = TRUE,
          float.env = "sidewaystable",
          no.space = TRUE,
          omit.stat=c("ser","f"),
          column.sep.width = "-10pt",
          label = "tab:modeltable",
          type = "latex",
          header = FALSE,
          initial.zero = FALSE,
          omit = c("teacherid"),
          omit.labels = c("Instructor fixed effect"))
```

```{r}
ols_plot_resid_qq(studentfirstsimilaritymodel)
```

```{r}
ols_plot_resid_fit(studentfirstsimilaritymodel)
```

```{r}
ols_plot_resid_hist(studentfirstsimilaritymodel)
```
